Globally-centered autocovariances in MCMC

### 2020-09-01 Paper/main.tex
Preliminary appendix fix

\begin{lemma}
\label{lemma: brownian}
(\cite{csorgo1981strong}). Suppose the conditions of Theorem~\ref{thm:kuelbs} hold, then for all $\epsilon > 0$ and for almost all sample paths, there exists $n_{0}\left(\epsilon\right)$ such that $\forall n\geq n_{0}(\epsilon)$ and $\forall i = 1, ..., p$

\[
\sup_{0\leq t \leq n-b_n}\sup_{0 \leq s \leq b_n} \left| B^{\left(i\right)}\left(t+s\right) - B^{\left(i\right)}\left(t\right) \right| < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\; \log\; n\right)\right)^{1/2} ,
\]
%
\[
\sup_{0 \leq s \leq b_n} \left|B^{\left(i\right)}\left(n\right) - B^{\left(i\right)}\left(n - s\right)\right| < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\;\log\;n\right)\right)^{1/2} , \; \textrm{and}
\]
%
\[
\left|B^{\left(i\right)}\left(n\right)\right| < \left(1+\epsilon\right)\sqrt{2n\;\log \log n} \; . 
\]
\end{lemma}

% \begin{lemma} \label{lemma:consis_1}
%   If Assumption~\ref{ass:sip} holds, then $\| \bar{\bar{X}} - \mu\|_{\infty}, \|\bar{X}_s - \mu\|_{\infty} \xrightarrow[]{a.s.} 0$ as $n \to \infty$ for all $s \in \{1,..., m\}$\\
%   \end{lemma}

% \begin{proof}
% Let $\|.\|$ denote the Euclidean norm. Assumption \ref{ass:sip} allows us to upper bound $\|\bar{X}_s - \mu\|_{\infty}$ using SIP. Following that, we show that the upper bound term converges to 0 as $n \to \infty$ using lemma \ref{lemma: brownian}.
%  \begin{align*}
%     \|\bar{X}_s - \mu\|_{\infty} & \leq \|\bar{X}_s - \mu\| \\
%     &= \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - n\mu\right\| = \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\
%     & \leq \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - \mu - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
%     &< \dfrac{D\psi(n)}{n} + \dfrac{\|L B(n)\|}{n}\\
%     &< \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| \left(\sum\limits_{i=1}^{p}|B^{(i)}(k)|^2\right)^{1/2}\\
%     & \leq \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}\\
%     & \xrightarrow[]{a.s.} 0\;\; as \;\; n\to \infty
%  \end{align*}
% %
% Similarly one can easily show that $\|\bar{\bar{X}} - \mu\|_{\infty} \to 0$ as $n \to \infty$ using the same upper-bound as:
% % 
% \begin{align*}
%     \|\bar{\bar{X}} - \mu\|_{\infty} & \leq \|\bar{\bar{X}} - \mu\| = \dfrac{1}{m}\left \|\sum_{j=1}^{m}(\bar{X}_j- \mu) \right\| \leq \dfrac{1}{m}\sum_{j=1}^{m}\|\bar{X}_j - \mu\| \xrightarrow{a.s.} 0 \, \textrm{as } n \to \infty 
% \end{align*}
% \end{proof}

@@

For the purpose of generalizing summations for positive and negative lags in the following proofs, we define the sets $I_k, J_{k1} \text{ and } J_{k2}$ as $ I_k := \{1, \dots, n-k\}, J_{k1} := \{n-k+1, \dots , n\}, J_{k2} := \{1, \dots, k\}$ for $k > 0$ and  $I_k := \{1-k, \dots, n\}, J_{k1} := \{1, \dots , -k\}, J_{k2} := \{n+k+1, \dots, n\}$ for $k < 0$. For $k=0$, $J_{k1}$ and $J_{k2}$ are empty sets and $I_k := \{1, \dots, n\}$. Notice that the empirical autocovariance estimator at lag-$k$ requires a summation over $I_k$.

@@

We can break $\hat{\Gamma}_{G,s}$ into four parts for all $k \geq 1$ as:
%  \[
%  \hat{\Gamma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\bar{X}_s - \bar{\bar{X}})(\bar{X}_s - \bar{\bar{X}})^T\,,
%  \]
% %
% where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$\\
% The expectation value of the first term is given by equation \ref{eq:priestly} and \ref{eq:song} while the other three terms contribute $o(1)$ terms.

 % \begin{proof}[Proof of Theorem~\ref{th:G-_expec}]
% \begin{lemma} \label{lemma:bias1}
% $\mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right] = \dfrac{m-1}{mn}\left(\sum\limits_{k=0}^{n-1}\Gamma(k) - \Sigma\right)$
% \end{lemma}
% \begin{proof}
% \begin{align*}
%     &\mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
%      &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
%     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
%     &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
%     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
%     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
%     &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,.
% \end{align*}
% %
% Similarly,
% %    
% \begin{align*}
%     \mathbb{E} \left[ \left(\bar{X}_1 - \bar{\bar{X}} \right)  \left(X_{11} - \bar{X}_1 \right)^T \right] &= \mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)^T\,.
%     % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
% \end{align*}
% \end{proof}

% \begin{lemma} \label{lemma:bias2}
% \[
% \mathbb{E}\left[\sum\limits_{s=1}^{m} \left(\bar{X}_{s} - \bar{\bar{X}} \right) \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] =  (m-1)\text{Var}(\bar{X}_1)\,.
% \]
% \end{lemma}

% % $\bar{X}_i$ are independently and identically distributed for all $i$; this implies $\Var(\bar{\bar{X}}) = \dfrac{1}{m} \Var(\bar{X}_1)$.

% \begin{proof}
% \begin{align*}
% \mathbb{E}\left[\sum_{s=1}^{m} \left(\bar{X}_{s} - \bar{\bar{X}} \right)  \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[\sum_{s=1}^{m}\bar{X}_{s}\bar{X}_{s}^{T} -\sum_{s=1}^{m}\bar{X}_{s}\bar{\bar{X}}^{T} - \bar{\bar{X}}^{T}\sum_{s=1}^{m}\bar{X}_{s}^{T} + m\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \mathbb{E}\left[\sum_{s=1}^{m}\bar{X}_{s}\bar{X}_{s}^{T} - m\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= m\left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
% &= m\left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
% &= (m-1)\Var(\bar{X_1})\,.
% \end{align*}
% \end{proof}

\begin{align*}
\hat{\Gamma}_{G,s}(k) & = \dfrac{1}{n}\sum_{t \in I_k} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
    &= \left[\dfrac{1}{n} \sum_{t \in I_k} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t \in J_{k1}}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\ 
    & \quad + \left[\dfrac{1}{n} \sum_{t \in J_{k2}} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right]   + \left[\dfrac{n-\abs{k}}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
    &= \hat{\Gamma}_s(k) - \dfrac{1}{n}\sum_{t \in J_{k1}}A_{st} - \dfrac{1}{n} \sum_{t \in J_{k2}}^{k}A_{st}^T  + \dfrac{n-\abs{k}}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
\end{align*}
%
where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$. Under the assumption of stationarity, we will study the expectations of each of the above terms. Without loss of generality, consider $A_{11}$,
\begin{align*}
    &\E \left[A_{11} \right]\\
     &= \mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
     % &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
    % &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,. \numberthis \label{eq:acf_2}
\end{align*}
%
Similarly,
%    
\begin{align}
\label{eq:acf_3}
    \mathbb{E} \left[ A_{11}^T \right] &= \mathbb{E}\left[ A_{11}\right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k)^T - n\text{Var}\left[\bar{X}_1 \right] \right)\,.
    % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
\end{align}

Further,
\begin{align*}
\mathbb{E}\left[ \left(\bar{X}_{1} - \bar{\bar{X}} \right)  \left(\bar{X}_{1} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{X}_{1}\bar{\bar{X}}^{T} - \bar{\bar{X}} \bar{X}_{1}^{T} + \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
&= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
&= \dfrac{m-1}{m}\Var(\bar{X}_1)\,. \numberthis \label{eq:acf_4}
\end{align*}
%
Additionally, the locally-centered autocovariance exhibits the following expectation (from \cite{priestley1981spectral})
 \begin{equation} \label{eq:priestly}
     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
 \right)\,.
 \end{equation}
%
Using\eqref{eq:acf_2}, \eqref{eq:acf_3}, \eqref{eq:acf_4}, and  \eqref{eq:priestly} in \eqref{eq:acf_breakdown},
\begin{align*}
    & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t \in J_{k1}}\mathbb{E}[A_{1t}] + \sum\limits_{t \in J_{k2}}\mathbb{E}[A_{1t}^T] \right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m}\,.
\end{align*}
%

 We can use the results of \cite{song1995optimal} to expand $\Var(\bar{X}_1)$. By proposition 1 in \cite{song1995optimal} 
\[
\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
\]

As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
 \begin{equation} \label{eq:G-ACF_expec_breakdown}
     \mathbb{E}\left[\hat{\Gamma}_{G,s}(k)\right] = \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2\,.
 \end{equation}
%
where,
\begin{align*}
    O_1 &= -\dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right)\right] + o(n^{-2})\, ,\\
    O_2 &= -\dfrac{1}{m}\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o(n^{-2})
\end{align*}
%
We observe that both $O_1 \textrm{ and } O_2$ are small order terms that converge to 0 as $n \to \infty$. Here, $O_1 = (\abs{k}/n)\mathcal{O}(1/n) \textrm{ and } O_2 = {\mathcal{O}}(1/n)$. For a diagonal element of $\Gamma$,
% We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term. This helps in countering the inherent negative bias in $\hat{\Gamma}(k)$ and give more informative estimates of autocovariance.  Although, bias term for a fixed $k$ is $o(1)$, it increases with $k$. We have explicitly written the end effect term arising from using the estimator $\bar{\bar{X}}$ for $\mu$. These are small order terms that vanish as $n \to \infty$.
%
\begin{align*}
& \E \left[ \hat{\Gamma}_{G,s}^{ii}\right]\\
& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)^{ii}\right] - \dfrac{\Var(\bar{X}_1)^{ii}}{m}\,.
\end{align*}
In the presence of positive correlation, the leftover term is positive.

>>>>

Let $B^{(i)}$ denote the $i$th component of the $p$-dimensional standard Brownian motion $B$.
\begin{lemma}
\label{lemma: brownian}
(\cite{csorgo1981strong}). Let $b_n$ be a sequence such that $b_n$ and $n/b_n \to \infty$ as $n \to \infty$. Then for all $\epsilon > 0$ and for almost all sample paths, there exists $n_{0}\left(\epsilon\right)$ such that $\forall n\geq n_{0}(\epsilon)$
\begin{align*}
 \sup_{0\leq t \leq n-b_n}\sup_{0 \leq s \leq b_n} \left| B^{\left(i\right)}\left(t+s\right) - B^{\left(i\right)}\left(t\right) \right| & < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\; \log\; n\right)\right)^{1/2} , \\ 
  \sup_{0 \leq s \leq b_n} \left|B^{\left(i\right)}\left(n\right) - B^{\left(i\right)}\left(n - s\right)\right|& < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\;\log\;n\right)\right)^{1/2} , \; \textrm{and} \\ 
  \left|B^{\left(i\right)}\left(n\right)\right|& < \left(1+\epsilon\right)\sqrt{2n\;\log \log n} \; . 
\end{align*}
%
\end{lemma}

@@

In order to generalize summations for positive and negative lags in the following proofs, we define the sets $I_k, J_{k1} \text{ and } J_{k2}$ as $ I_k := \{1, \dots, n-k\}, J_{k1} := \{n-k+1, \dots , n\}, J_{k2} := \{1, \dots, k\}$ for $k > 0$ and  $I_k := \{1-k, \dots, n\}, J_{k1} := \{1, \dots , -k\}, J_{k2} := \{n+k+1, \dots, n\}$ for $k < 0$. For $k=0$, $J_{k1}$ and $J_{k2}$ are empty sets and $I_k := \{1, \dots, n\}$. Notice that the empirical autocovariance estimator at lag-$k$ requires a summation over $I_k$.

@@

We can break $\hat{\Gamma}_{G,s}$ into four parts for all $k \geq 1$ as:
%
\begin{align*}
\hat{\Gamma}_{G,s}(k) & = \dfrac{1}{n}\sum_{t \in I_k} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
    &= \left[\dfrac{1}{n} \sum_{t \in I_k} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t \in J_{k1}}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\ 
    & \quad + \left[\dfrac{1}{n} \sum_{t \in J_{k2}} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right]   + \left[\dfrac{n-\abs{k}}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
    &= \hat{\Gamma}_s(k) - \dfrac{1}{n}\sum_{t \in J_{k1}}A_{st} - \dfrac{1}{n} \sum_{t \in J_{k2}}^{k}A_{st}^T  + \dfrac{n-\abs{k}}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
\end{align*}
%
where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$. Under the assumption of stationarity, we will study the expectations of each of the above terms. Without loss of generality, consider $A_{11}$,
\begin{align*}
    &\E \left[A_{11} \right]\\
     &= \mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
     % &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
    % &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,. \numberthis \label{eq:acf_2}
\end{align*}
%
Similarly,
\begin{align}
\label{eq:acf_3}
    \mathbb{E} \left[ A_{11}^T \right] &= \mathbb{E}\left[ A_{11}\right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k)^T - n\text{Var}\left[\bar{X}_1 \right] \right)\,.
    % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
\end{align}

Further,
\begin{align*}
\mathbb{E}\left[ \left(\bar{X}_{1} - \bar{\bar{X}} \right)  \left(\bar{X}_{1} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{X}_{1}\bar{\bar{X}}^{T} - \bar{\bar{X}} \bar{X}_{1}^{T} + \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
&= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)= \dfrac{m-1}{m}\Var(\bar{X}_1)\,. \numberthis \label{eq:acf_4}
\end{align*}
%
Additionally, $\hat{\Gamma}_s(k)$ exhibits the following expectation (from \cite{priestley1981spectral})
 \begin{equation} \label{eq:priestly}
     \mathbb{E}[\hat{\Gamma}_s(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
 \right)\,.
 \end{equation}
%
Using\eqref{eq:acf_2}, \eqref{eq:acf_3}, \eqref{eq:acf_4}, and  \eqref{eq:priestly} in \eqref{eq:acf_breakdown},
\begin{align*}
    & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t \in J_{k1}}\mathbb{E}[A_{1t}] + \sum\limits_{t \in J_{k2}}\mathbb{E}[A_{1t}^T] \right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m}\,.
\end{align*}
%

By \cite[Proposition 1]{song1995optimal} 
\[
\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
\]

% As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
Consequently,
 \begin{equation} \label{eq:G-ACF_expec_breakdown}
     \mathbb{E}\left[\hat{\Gamma}_{G,s}(k)\right] = \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2\,.
 \end{equation}
%
where,
\begin{align*}
    O_1 &= -\dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right)\right] + o(n^{-2})\, ,\\
    O_2 &= -\dfrac{1}{m}\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o(n^{-2})
\end{align*}
%
Here $O_1 = (\abs{k}/n)\mathcal{O}(1/n) \to 0 \textrm{ and } O_2 = {\mathcal{O}}(1/n) \to 0$ as $n \to \infty$. For a diagonal element of $\Gamma$,
% We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term. This helps in countering the inherent negative bias in $\hat{\Gamma}(k)$ and give more informative estimates of autocovariance.  Although, bias term for a fixed $k$ is $o(1)$, it increases with $k$. We have explicitly written the end effect term arising from using the estimator $\bar{\bar{X}}$ for $\mu$. These are small order terms that vanish as $n \to \infty$.
%
\begin{align*}
& \E \left[ \hat{\Gamma}_{G,s}^{ii}\right]\\
& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)^{ii}\right] - \dfrac{\Var(\bar{X}_1)^{ii}}{m}\,.
\end{align*}
In the presence of positive correlation, the leftover term is positive.
